---
title: "Practical Considerations for Fourier Transforms of Data Sets"
author: "Chris Hering"
date: "1/26/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE) 
library(e1071)
```


This is a short guide intended to shed some light on a few fundamental concepts in Fourier analyses. After reading this, you will hopefully feel more comfortable working in the frequency domain and be able to gain quick insights about the frequency content of time domain signals. Also, you will be able to tell if a data set is appropriate for running through a Fourier transform. For that to happen, we will need to focus on issues commonly encountered with plant / process data sets. These issues can be placed into one of three catagories:

* data acquisition

* data transformations

* spectra interpretability

This guide will discuss the qualities which can make or break a data set's elegibility for frequency domain analysis, run through an example, and then review the techniques used in the example.


## Inputs and Outputs
The outputs (generated frequency spectra) can only be as good as the inputs. Fourier transform algorithms usually require that their input data sets meet a few criteria, otherwise the results can be completely useless or misleading. These qualities of their inputs, and their respective criteria, are discussed below.


## Qualities of a Data Set

### Sampling Rate

If your data set was acquired using an inappropriate sampling rate/frequency, you will not be able to retrieve useful frequency domain info. This is just a consequence of obtaining data  through discrete processing systems. More specifically, you will not be able to pick up any frequencies greater than 2 * the sampling frequency (fs); at least two points per cycle are needed to identify a sine wave. 2*fs is known as the Nyquist Frequency. 

Below, you can see the impact that sampling at a quicker rate has on the resulting frequency spectrum. The time domain signal being evaluated is composed of superimposed sine waves at .1, 1, and 2 Hz. 

```{r, echo=FALSE}

inputPanel(
  
  selectInput("fs1", label = "Sampling Frequency (Hz)",
              choices = c(1, 3, 5, 7), selected = 1)

)


renderPlot({
  
  
f1 <- 1
f2 <- .1
f3 <- 2
fs <- as.numeric(input$fs1)
fNy <- fs/2
ts <- 1/fs

t <- seq(by=ts, length.out=1000)
x <- (10*(sin(2*pi*t*f1)) + 5*sin(2*pi*t*f2) + 15*sin(2*pi*t*f3)) 

fft <- fft(x)
fft.y <- Mod(fft)
fft.x <- seq(1,length(fft), 1) 
fft.x <- fft.x[1:length(fft)/2]*fs/length(fft)       #Convert bins to frequencies
fft.y <- fft.y[1:length(fft)/2]/(length(fft)/2)       #Scale magnitudes
  plot(fft.x, fft.y, xlab='Freq (Hz)', ylab='Magnitude', type="l")
  
})
```

Note how at slow sampling frequencies, some waves are missed by the resulting spectra. Also, the spectra end at 1/2 the selected sampling frequency; going beyond this results in a mirrored image about a vertical axis at the Nyquist frequency. 


### Amount of Data
Some less intuitive properties of periodograms and frequency spectra are related to the number of data points in the processed time domain signal. First, the number of points in the time domain signal will be equal to the number of points output by the FFT algorithm. Additionally, for a given sampling frequency, increasing the number of points out of the FFT (N) will increase the frequency resolution of the spectrum. The output of most DFT algorithms are indexed where each value represents a frequency bin. You can easily calculate that bandwidth as it's the ratio fs:N. The number of points in your time domain signal (and consequently your FFT output) thus affects the frequency resolution. For a given sampling frequency, a larger time domain will give you more resolution. 

So it looks like using a large vector would be ideal. However, in practical scenarios this is not true. For a pure sine wave, or combination of sine waves, using a larger vector will improve your resolution and frequency spectrum. However, real processes are plagued by noise and external disturbances. These can corrupt an otherwise acceptable (clean sine waves) sample of data. On top of that, the periodogram (most common version of a given frequency spectrum) is an inconsistent estimator of the power spectrum of a data set. Using a larger sample size does not cause the variance to converge, but rather diverge. The result is, inevitably, a noiser periodogram. 

```{r noise, echo=FALSE}

noise <- seq(0,20/.01,by=1)

for (x in 1:length(noise)) 
  {
 noise[x] <- rnorm(1,0,3.5)
}

```


```{r, echo=FALSE}

inputPanel(
  
  sliderInput("tf", label = "Length of Time Signal (s)",
              min = 2, max = 20, value = 5, step = 1)
)


renderPlot({
  
f1 <- 4
f2 <- 20
f3 <- 3
tf <- input$tf 
fs <- 100
fNy <- fs/2
ts <- 1/fs


t <- seq(from = 0, to = tf, by=ts)
x <- (10*(sin(2*pi*t*f1)) + 5*sin(2*pi*t*f2) + 15*sin(2*pi*t*f3) + noise[1:tf/ts-1]) 

  plot(t, x, type="l", xlab='Time (s)', ylab='Amplitude')

})

renderPlot({
  

f1 <- 4
f2 <- 20
f3 <- 3
tf <- input$tf 
fs <- 100
fNy <- fs/2
ts <- 1/fs

t <- seq(from = 0, to = tf, by=ts)
x <- (10*(sin(2*pi*t*f1)) + 5*sin(2*pi*t*f2) + 15*sin(2*pi*t*f3) + noise[1:tf/ts-1]) 

fft <- fft(x)
fft.y <- Mod(fft)
fft.x <- seq(1,length(fft), 1) 
fft.x <- fft.x[1:length(fft)/2]*fs/length(fft)       #Convert bins to frequencies
fft.y <- fft.y[1:length(fft)/2]/(length(fft)/2)       #Scale magnitudes
  plot(fft.x, fft.y, xlab='Freq (Hz)', ylab='Magnitude', type="l")
  
})
```

The above time signal is composed of sine waves at 3 different frequencies. Because only white noise was added, the spectrum doesn't get too noisy, but you do see the development of random peaks in the frequency spectrum. In real data sets, the noise can overwhelm the true peaks. In this case, using the shortest time signal results in the least ambiguous spectrum, but the resolution is poor.


### Stationarity
Technically, periodograms are quick estimates of *stationary* population time series. As always in statistics, we sample from the population and try to project calculations from the sample to the population. For the purposes of this application, it is important that our sample retains some degree of stationarity - that its statistical properties remain somewhat constant. Some dead giveaways that your time signal is not stationary are if:

* the average value (of 1, 5, 20 etc. minute intervals) changes over time
* the variance changes over time
* there is autocorrelation

Given these criteria, control loops can be great candidates for a good data set. If what you are looking at is not controlled, or if there are frequent significant external disturbances, then you may still be able to find a workable data set if you begin looking for one which fits the above description. Next, we will look at an example of decomposing  a time domain signal of an oscillatory level control loop in a black liquor crystallization unit.


## Example
Now we will look at a time series sampled from a level control loop. The vessel under investigation is an about 16,000 gallon flash chamber. We have the level process variable as well as the set point of the control loop.

To start, we should look at a graph of the data. This data were acquired by reading 2000 points from the historian at its fastest sampling rate, 1 minute. Keep in mind that, because the data were sampled every minute, we won't be able to pick up oscillations faster than 30 seconds. For a level loop, this should be fine. 

```{r, echo=FALSE}
Chamber.Lvl <- c(55.7092514, 56.41423035, 56.8689537, 57.16956329, 57.88369751, 
58.24533844, 56.44017029, 56.31198883, 56.04647827, 55.7382431, 
55.55436707, 55.29953766, 55.30869675, 55.30487823, 55.47883606, 
55.57115173, 55.48722839, 55.46662903, 55.49714661, 55.15610123, 
55.34531784, 56.01824951, 56.56605911, 56.56910706, 56.64846039, 
57.05511856, 57.02993774, 56.89489365, 56.86666489, 57.5037384, 
56.36463547, 56.07318115, 55.20645905, 55.29954147, 55.12100601, 
54.33439255, 54.14365005, 54.67391205, 55.59862137, 56.58055496, 
56.22272491, 56.07165909, 56.14109039, 56.49891663, 57.05358887, 
57.18100357, 57.0596962, 56.67134476, 56.29825592, 56.05944824, 
55.61845779, 55.99078369, 55.60091019, 55.55589294, 55.77867889, 
54.84175873, 54.75783539, 54.7097702, 55.31555939, 55.74434662, 
56.28528595, 56.36616135, 56.91549683, 57.52738953, 57.32749176, 
56.62785721, 56.61488724, 56.5004425, 56.41575623, 56.24332428, 
55.81835175, 55.05996704, 54.88830185, 54.93942261, 54.89746094, 
55.58259964, 55.79012299, 56.48060608, 56.49205017, 56.21738434, 
56.55461121, 57.05130005, 55.71840668, 55.71993256, 55.52766418, 
55.69399261, 55.81987762, 55.96865845, 56.44474792, 56.58818436, 
55.70314407, 55.61616898, 55.31250763, 55.57267761, 55.87557602, 
56.18152618, 56.3150444, 56.39744186, 56.1723671, 55.91219711, 
56.07394409, 56.05487442, 56.32572556, 56.48518372, 56.48136902, 
57.17261505, 56.78121185, 55.76952362, 55.18967056, 54.81352997, 
54.92111206, 55.00732422, 55.86031723, 56.28834152, 56.56758499, 
56.34784698, 55.67797089, 55.2964859, 56.09149551, 56.67134476, 
57.42134094, 56.86132431, 57.25730133, 56.00985718, 55.74358368, 
55.38956833, 55.1690712, 54.9279747, 54.54115295, 54.98977661, 
55.54521179, 56.37379074, 56.93227768, 56.74306488, 56.34708786, 
55.77181244, 55.54978943, 55.99841309, 56.89718246, 58.55281448, 
57.63420486, 56.54469681, 55.67110443, 54.88372803, 54.86236191, 
55.19425201, 55.38651657, 55.38956833, 55.01190186, 54.54344177, 
54.81429291, 55.0920105, 56.08081055, 57.11996841, 57.52662659, 
57.299263, 56.94906616, 56.76900482, 56.66524506, 57.69219208, 
57.57774353, 57.00552368, 56.24408722, 54.95239258, 53.63704681, 
53.00683594, 53.44019699, 54.17264175, 55.11261368, 56.21738434, 
56.58971024, 56.48976135, 56.49815369, 56.32191086, 56.71865082, 
57.50297546, 58.95031738, 58.85876083, 58.2773819, 57.09860229, 
56.13269424, 55.35599899, 54.52589417, 53.51268005, 54.50453186, 
53.87737656, 53.36542892, 54.3008194, 55.06225586, 56.01824951, 
56.4058342, 57.09631729, 58.56044006, 59.0144043, 57.93557358, 
57.06350708, 56.63090897, 56.16474152, 56.38829041, 56.31733322, 
56.07012939, 54.34659576, 52.82982635, 52.78710175, 53.99105835, 
54.46638489, 55.4277153, 56.70720673, 57.34122467, 58.02636719, 
58.22168732, 57.48161316, 57.90811157, 57.16574478, 56.93991089, 
57.1428566, 56.10446548, 55.51927185, 54.28174591, 53.42417526, 
53.61873245, 53.88653183, 54.38093185, 54.7677536, 55.23926544, 
56.11133194, 56.95288086, 58.17056656, 59.20590973, 58.70998001, 
58.72066498, 58.47346497, 57.75170135, 56.78655243, 55.5375824, 
55.04241943, 54.00479126, 52.7146225, 53.49208069, 53.05413818, 
54.40610886, 55.26215363, 55.26291656, 55.53605652, 55.39338303, 
56.16016388, 57.49229431, 58.54976273, 58.46888733, 58.2735672, 
58.30561066, 57.57621765, 57.0406189, 56.10217667, 56.17618179, 
54.63042068, 54.09482193, 52.88857651, 52.30109406, 53.62407303, 
54.42365646, 55.89846802, 56.84529877, 56.99942017, 56.48442078, 
56.45237732, 57.07189941, 58.07366943, 57.86156464, 58.33078766, 
57.62352371, 57.08029175, 56.53401184, 55.68102264, 55.35676193, 
54.4221344, 54.68001175, 54.27945709, 54.60448074, 54.77462006, 
54.79521942, 55.26139069, 55.16678619, 56.58207703, 56.9093895, 
56.74230194, 56.22653961, 56.88116074, 57.57240295, 57.62276077, 
58.19879913, 56.80638885, 55.96560287, 55.39185715, 54.55870056, 
54.63118362, 55.17746735, 55.07904434, 55.13550568, 54.85625839, 
55.03555298, 54.56022644, 55.26673126, 56.9246521, 57.08105469, 
56.92617798, 56.5813179, 56.48976135, 56.52561951, 56.88911819, 
56.95843506, 57.85120773, 57.07647705, 56.68202972, 56.34708786, 
55.92822266, 55.48112488, 54.97528076, 54.51695633, 53.46995544, 
53.24030304, 53.99868774, 54.90432739, 55.79088593, 56.5370636, 
57.42438889, 57.90047836, 57.45033264, 58.22473907, 57.96838379, 
57.8470726, 57.57622147, 56.53096008, 55.21866608, 54.63423538, 
54.41602707, 54.77233124, 55.6802597, 55.09964371, 54.6113472, 
54.32523346, 53.92849731, 55.4025383, 56.86590195, 56.99789429, 
57.26340485, 57.18787384, 56.77358246, 56.4287262, 56.84072495, 
57.09097672, 57.18405533, 56.06479263, 55.95874023, 55.5085907, 
55.7634201, 55.78325653, 54.77462006, 54.8057518, 55.03982925, 
55.37234879, 55.56565857, 56.0753212, 56.12231827, 56.47816467, 
56.61671829, 56.71376419, 56.76442719, 57.16727066, 56.96203613, 
56.72322845, 55.90380859, 55.42161179, 54.99069214, 55.4594574, 
55.38422775, 55.29343414, 55.46815491, 55.51011658, 55.15381622, 
55.19577789, 55.73519135, 55.91372299, 56.85826874, 56.3478508, 
56.61565018, 57.03451538, 57.0810585, 57.54798889, 57.64030838, 
57.08258438, 55.72603607, 55.05386353, 54.89135361, 55.13626862, 
54.93255234, 54.389328, 54.65941238, 54.99130249, 55.20264435, 
55.82140732, 57.21686554, 57.51670837, 57.40302658, 56.66753006, 
56.45085144, 55.83971786, 56.18686676, 56.79875946, 56.44779968, 
55.55207825, 54.47859192, 54.34888458, 56.14108658, 56.99026489, 
57.48924255, 57.67769623, 56.38829041, 55.91296387, 55.54445267, 
55.21256256, 55.8694725, 55.85115814, 55.90685654, 55.27283478, 
55.91296387, 56.09836197, 56.26850128, 56.08920288, 56.08615494, 
55.3521843, 54.93713379, 55.48799133, 56.26621246, 56.87429428, 
57.11233902, 56.63014603, 56.06784439, 55.45060349, 55.66805267, 
56.50273132, 55.92593384, 56.42338181, 55.85573959, 55.92440796, 
56.06784439, 56.13650894, 55.79927826, 56.05563736, 56.22882843, 
55.22553253, 54.75859833, 54.82421112, 55.17822647, 55.59480286, 
55.96408081, 56.8803978, 56.8803978, 56.99789429, 56.38294601, 
56.7957077, 56.77739716, 56.49891663, 56.26850128, 56.26010895, 
54.76622772, 55.40787888, 55.71001434, 56.24027252, 55.56504822, 
55.82064438, 55.62379837, 55.26825714, 55.89083481, 56.37913132, 
56.56911087, 56.38523483, 55.85573959, 55.46052551, 55.43305969, 
55.8771019, 56.46611023, 56.67363358, 57.07876968, 56.741539, 
56.4500885, 55.96408081, 56.46000671, 56.44703293, 55.64211273, 
55.40482712, 55.41474533, 55.56657791, 55.79317474, 55.94958496, 
55.38728333, 55.52613831, 55.54978943, 55.86565781, 56.18152618, 
56.21967316, 55.90761948, 55.91601181, 55.77028656, 55.56047058, 
55.72832489, 56.39591599, 56.35776901, 56.76366425, 56.50654602, 
56.26621246, 56.27307892, 55.94424057, 56.74382782, 56.43482971, 
55.96102905, 55.03936768, 55.30182648, 55.17212296, 55.30716705, 
55.22782135, 54.97070313, 54.86541367, 55.06225586, 55.92898178, 
56.81935883, 57.75017548, 58.10876846, 57.80205536, 57.13675308, 
56.92159653, 57.30384064, 57.07571411, 56.71941376, 55.82827377, 
55.31632614, 54.71205902, 54.03378296, 53.89339828, 53.91857529, 
54.02767944, 54.51826477, 55.454422, 55.79012299, 56.59886551, 
56.78197479, 57.40608215, 57.92412949, 57.90581894, 57.40836716, 
57.21457672, 56.70339203, 56.79647446, 55.84734726, 55.93814087, 
55.46205139, 54.36262131, 54.65864944, 54.72274017, 55.44297409, 
55.25452423, 54.96688843, 54.3740654, 54.83565903, 55.79012299, 
57.03560638, 58.07748413, 58.12860489, 57.39539719, 57.48085022, 
56.41651917, 55.9289856, 55.27359772, 55.12939835, 55.39109421, 
55.49485779, 55.89377975, 55.97369003, 55.80309296, 55.75862503, 
54.94029236, 55.77595139, 56.14923859, 56.38503265, 56.35853195, 
56.38370895, 56.546875, 56.42597961, 55.91173935, 55.65477371, 
55.84490585, 56.19830704, 56.47144699, 56.91030502, 56.93411255, 
56.84682846, 55.8732872, 55.35752487, 55.18448257, 55.5677948, 
55.4683075, 55.01693726, 55.06027603, 55.5009613, 55.1475563, 
55.66850662, 55.38315964, 56.21417999, 56.67440033, 56.66890335, 
57.18558502, 56.54896545, 56.56971741, 56.69210052, 56.36005783, 
56.085392, 55.5476532, 55.23575592, 55.43595505, 55.60380936, 
55.85619736, 56.09241104, 55.95049667, 55.70909882, 55.72954559, 
56.01489258, 56.06219482, 56.71620941, 57.56554031, 57.33176804, 
57.45140076, 56.29444504, 56.17084122, 55.94225693, 55.42405319, 
55.32304001, 54.77767181, 54.93697739, 55.01663208, 55.03189087, 
54.34827805, 54.99649048, 55.3697319, 55.94713974, 56.37287521, 
56.64082718, 57.00064087, 56.13879776, 57.06961441, 57.43888474, 
57.69829559, 57.39219284, 56.48396301, 55.57847977, 54.77004623, 
54.07208252, 54.20453644, 55.17471695, 56.35609055, 56.66066742, 
57.03237915, 56.33197784, 56.04388428, 56.08630371, 56.39454269, 
56.97897339, 56.68416595, 55.99139404, 54.54542542, 54.11328506, 
54.87075424, 55.48814392, 56.3679924, 56.94845581, 57.38792038, 
56.65639496, 55.77288055, 54.94613647, 54.93911362, 55.71916962, 
56.73787689, 57.58476639, 57.51914978, 56.60817337, 55.85955048, 
55.79851532, 54.87899399, 55.14511871, 55.71215057, 56.01428223, 
55.97705078, 55.84673309, 55.8845787, 55.73656464, 56.11743546, 
56.26758575, 55.86108017, 55.82079697, 56.33563995, 56.35120773, 
56.01916504, 55.98681641, 55.37217331, 55.58977127, 55.84093857, 
56.26331329, 56.05792236, 56.86086655, 56.25873566, 56.08569717, 
55.96057129, 56.08355713, 56.78029633, 56.63533401, 56.48884583, 
56.04541016, 55.74449921, 55.34287643, 54.99984741, 54.89181137, 
55.01358032, 55.74480438, 56.10156631, 55.72618866, 56.00177002, 
56.12079239, 56.21906281, 56.22028351, 56.24195099, 56.12506485, 
56.35425949, 56.55628967, 56.68050385, 56.93655014, 56.45741272, 
56.39759445, 55.96087646, 55.03463745, 54.67238235, 54.35254669, 
55.25315094, 55.5665741, 56.07562637, 56.43787766, 55.79637909, 
56.50776672, 56.53218079, 56.80898285, 56.71529007, 57.13980484, 
56.76564789, 56.25324249, 56.23401642, 56.07196426, 55.26963043, 
55.23758698, 55.38682175, 55.26902008, 55.49516296, 55.66423416, 
56.11957169, 55.67125702, 55.7231369, 55.91967392, 56.27033234, 
56.09729385, 55.97857666, 56.38904953, 56.22486115, 56.91213608, 
57.44651794, 57.21121979, 56.12384415, 55.55711746, 55.07645035, 
55.23941803, 55.59281921, 55.8491745, 55.44266891, 55.5830574, 
55.44724655, 54.87533188, 54.93606186, 55.59281921, 56.4650383, 
57.55332947, 57.48771667, 57.19351959, 56.62465286, 56.02587891, 
56.03167725, 56.17938614, 56.04541397, 55.95324707, 55.25589752, 
55.4203949, 54.56251907, 54.68947601, 55.22202301, 55.2574234, 
55.91814804, 56.17297745, 56.52729797, 56.9069519, 57.46055603, 
56.82424545, 57.54173279, 57.66228485, 57.04855728, 55.96209717, 
55.34287643, 55.05996704, 54.62355423, 54.26770782, 54.44044113, 
54.72731781, 54.63209915, 55.20889664, 55.83636093, 56.38203049, 
56.46656799, 56.88802719, 56.76778412, 57.65129471, 58.30927277, 
58.23206329, 57.31162643, 56.34449005, 55.0743103, 54.65773392, 
55.76677704, 56.32526779, 56.45100021, 55.61601639, 54.03149414, 
53.10922623, 53.78673553, 55.02182007, 56.95089722, 57.48100281, 
56.65761566, 55.52812576, 54.94155502, 55.3874321, 56.12933731, 
57.98272705, 59.02249146, 58.73561859, 58.41212082, 57.3940239, 
55.78203583, 55.48722839, 54.11267471, 53.67808914, 54.19477081, 
54.67390823, 54.81215668, 55.38682175, 55.69994354, 55.80248642, 
55.64348221, 55.84002304, 56.70613861, 56.84469223, 56.90054321, 
56.5712471, 56.33228683, 56.00146484, 56.35700607, 56.69301605, 
56.78609467, 56.92892456, 56.56330872, 56.21631622, 55.23026276, 
54.90676498, 54.70168304, 54.69039154, 54.9229393, 55.56809998, 
55.99261475, 56.30329132, 57.21762848, 56.61122513, 56.45100403, 
56.2077713, 56.718647, 56.44672775, 56.26667023, 55.66820526, 
56.00054932, 56.47267151, 56.20105743, 55.71153641, 55.6611824, 
55.29160309, 55.10239029, 56.15100479, 56.37958908, 56.43940353, 
56.56727982, 55.98040771, 55.97949219, 56.02923584, 55.6007576, 
55.6840744, 55.51011658, 55.59556961, 55.65690994, 55.57695389, 
56.0032959, 56.23004913, 56.71498871, 56.51387024, 56.53553772, 
56.31672287, 56.668293, 56.61244583, 56.59840775, 56.42353439, 
54.63118362, 54.92080307, 55.27481842, 55.74297333, 55.51316833, 
56.03503418, 56.68508148, 56.59688187, 56.67317581, 56.53004837, 
56.0551796, 56.39637375, 56.46290588, 56.47175598, 56.7036972, 
56.54652405, 56.19281769, 55.83941269, 55.28305817, 54.6037178, 
55.0642395, 55.20737457, 54.470047, 55.10543823, 55.94256592, 
56.77602386, 57.37418747, 57.45750046, 57.48558044, 56.2480545, 
56.6216011, 55.8745079, 55.29282761, 54.99191284, 55.17288971, 
55.44206238, 55.69353104, 55.78874969, 56.13238907, 56.23188019, 
56.61061478, 56.89474106, 56.20410538, 56.10614395, 55.86260605, 
55.66088104, 55.97918701, 56.68416595, 56.59352493, 55.9300499, 
55.13992691, 55.04043579, 55.37308884, 56.36890793, 56.76259613, 
57.18527603, 56.81386948, 56.37348557, 55.54612732, 54.48103333, 
54.49324036, 55.77806854, 57.54020691, 57.85180283, 57.82921982, 
57.03756714, 55.77196503, 55.27207184, 56.5080719, 59.05209732, 
60.83315659, 60.04364014, 57.6689949, 55.2851944, 54.82040024, 
55.81804657, 57.04489136, 59.09909439, 58.83053207, 56.76747894, 
54.25244904, 53.17972565, 54.25733185, 56.48182678, 58.86654282, 
60.52766418, 59.5873909, 58.0919838, 55.93859863, 54.6983223, 
54.93819809, 58.16980362, 56.56300354, 55.10269547, 54.47218323, 
55.19516754, 57.43705368, 59.34995651, 59.39237595, 57.9720459, 
56.46351624, 55.83452606, 55.61449051, 55.85467148, 57.08151627, 
57.13034439, 58.10418701, 58.33704758, 57.3284111, 56.27094269, 
56.56391907, 56.47602844, 56.69515228, 57.23227692, 56.95150375, 
57.3183403, 57.0848732, 56.87948227, 56.06768799, 56.23432159, 
56.07806778, 56.50196838, 56.7882309, 57.89574814, 57.74254608, 
57.39310837, 56.52333069, 56.32038498, 56.31550217, 59.22605133, 
59.42442322, 57.38029099, 57.90307236, 58.18262482, 58.59279251, 
58.03979492, 57.73522186, 56.55751419, 55.89068222, 56.18579483, 
56.18304825, 57.20999908, 56.96005249, 56.60786819, 56.70643997, 
56.26514435, 56.58711624, 57.50205994, 58.4756012, 58.51832581, 
58.17651749, 57.24356842, 56.19098663, 55.74816132, 56.22058487, 
56.99362183, 58.23206329, 58.60896683, 58.31446457, 57.34915924, 
56.30390167, 55.48753357, 55.25955963, 55.61021805, 56.62129593, 
57.38059616, 57.19229889, 58.00622559, 57.806633, 58.34070969, 
57.69463348, 57.64091873, 56.88436508, 57.41691208, 57.32230377, 
57.13003922, 56.80562973, 56.86544418, 56.15039444, 55.83483505, 
55.78142548, 55.96453857, 55.36576462, 56.14825821, 56.89596176, 
57.54081726, 57.57439041, 58.39289474, 59.22147369, 58.28638458, 
58.50276184, 57.98608398, 57.71721268, 57.06320572, 56.10858536, 
55.76647186, 55.87969589, 55.92150497, 56.11926651, 55.40055466, 
55.7533493, 55.65324783, 56.12994766, 57.13217545, 57.6198616, 
58.51496887, 58.38984299, 58.1133461, 57.25150299, 57.24906158, 
58.22382355, 58.18628693, 57.70684052, 57.53227234, 56.43055344, 
56.56269836, 55.94470215, 55.86382675, 56.06219482, 56.23432159, 
56.58039856, 56.83767319, 56.91335678, 56.84988022, 57.27591705, 
57.4697113, 57.47093201, 57.60429764, 57.46086121, 57.64183426, 
56.8437767, 57.74498749, 57.93115234, 57.28110504, 56.79189301, 
56.12903214, 55.97277832, 55.76921844, 55.90685654, 56.6924057, 
57.46788025, 57.90307236, 57.59880447, 57.29605865, 57.64305496, 
57.6488533, 57.38669968, 57.21274567, 57.02932739, 56.96768188, 
56.02832031, 56.53797913, 56.64754105, 56.76198578, 57.02810669, 
57.13309097, 57.01956177, 56.42444992, 56.62373734, 56.71804047, 
56.97897339, 56.69759369, 57.14804459, 57.34916306, 57.78435516, 
57.58293152, 57.69097137, 57.85882187, 57.43522263, 57.35099411, 
57.04123306, 56.66371536, 57.1440773, 56.26117706, 56.9307518, 
56.37440109, 56.06219864, 55.89464951, 56.11651993, 56.86880112, 
56.61458206, 57.41844177, 57.6995163, 57.51487732, 57.47154236, 
57.45475388, 56.61397171, 57.1037941, 57.01589966, 57.66106033, 
57.46177673, 57.56340408, 57.14316177, 57.23410797, 56.83065414, 
56.24408722, 55.84734726, 56.43238449, 57.0519104, 57.42088318, 
56.9698143, 56.41041183, 55.94958115, 55.7899704, 56.51905823, 
57.51457214, 58.40571213, 59.0786438, 58.97640991, 58.73714447, 
57.68364716, 57.54753113, 57.39463425, 57.42515182, 57.15597916, 
56.22303009, 55.73107147, 54.92934799, 55.29831696, 55.08774185, 
54.72701263, 55.67369461, 56.07715225, 56.77724457, 57.50236511, 
58.42798996, 58.67580032, 58.87600327, 58.71944427, 58.31903839, 
58.20093155, 58.18292999, 58.37885666, 58.09900284, 57.55577087, 
56.14154434, 55.05020142, 54.81307602, 55.5589447, 55.33250046, 
55.98010254, 56.57735062, 56.64265823, 56.83065414, 56.8993187, 
57.02597046, 57.86919785, 57.71569061, 57.07663345, 57.64336014, 
57.5682869, 57.672966, 58.6068306, 59.06521606, 58.35505295, 
57.09830093, 57.1758194, 57.31009674, 57.22861481, 56.72933197, 
56.19159698, 56.2947464, 54.79994965, 53.8050499, 54.02020264, 
54.90554428, 56.7503891, 57.65495682, 58.20581818, 58.23511505, 
58.49208069, 58.4780426, 58.76033783, 58.74385834, 58.62117386, 
58.13806534, 57.13370132, 56.29657745, 55.53788757, 55.59801102, 
55.8909874, 56.19556427, 56.13879776, 55.93157578, 55.46922302, 
55.58031082, 56.4980011, 57.88048935, 59.22483063, 59.60722733, 
58.95840454, 58.82534409, 56.95211792, 57.33908844, 57.9088707, 
57.69402313, 57.61955643, 56.23065948, 54.45661926, 52.4848175, 
53.21421051, 55.29038239, 56.95486069, 58.39320374, 59.18576813, 
59.0548439, 57.44621277, 56.87673569, 57.29972076, 57.92596436, 
58.41181564, 58.4060173, 58.02178955, 57.94854736, 57.7587204, 
56.19281769, 55.86718369, 56.21906281, 56.09088516, 56.18518448, 
55.41917419, 54.79842377, 54.76943207, 55.45396042, 56.43238449, 
57.30338669, 58.39381027, 59.56267166, 58.73439789, 59.5821991, 
58.39777756, 58.27021027, 58.28638458, 57.8408165, 56.72048187, 
54.42579269, 54.05652237, 54.48377991, 55.46464157, 56.23432159, 
57.19290924, 57.22342682, 57.4382782, 58.20825958, 58.50276184, 
58.637043, 58.6471138, 57.26889801, 57.57621765, 56.80165863, 
56.15955353, 56.16016006, 56.94265366, 56.36951828, 55.91936874, 
56.15710831, 56.11316299, 57.07815933, 55.96667099, 56.00085449, 
56.04236221, 57.77214813, 58.65169144, 58.72768402, 59.1735611, 
58.6913681, 56.92739487, 56.64143753, 56.74245453, 56.93441391, 
56.76747894, 56.62526321, 55.88488388, 56.44337463, 55.43198776, 
54.95650864, 56.32618332, 56.71590424, 57.09249878, 57.59636307, 
56.89535141, 56.89901352, 58.35596848, 58.94711304, 59.05941772, 
58.81099701, 57.85302353, 55.89983749, 55.51683044, 57.24784088, 
57.51487732, 57.48985291, 57.11996841, 55.29373932, 54.3211174, 
54.5002594, 54.92141342, 56.15436172, 57.2753067, 58.1841507, 
58.47407532, 58.43379211, 58.63124466, 59.84130478, 58.76308441, 
58.38526535, 57.60948563, 56.58070755, 55.69200516, 55.0328064, 
54.90737534, 54.96170044, 55.54002762, 55.97704697, 56.24378204, 
56.34022141, 56.85934067, 57.44651794, 58.75270844, 58.93948364, 
59.0105896, 58.47712708, 57.89208603, 57.3461113, 57.45963669, 
57.23258209, 57.15475845, 56.78823471, 55.93280029, 55.19455719, 
55.22019196, 55.13656998, 55.89709091, 56.71376419, 57.18069839, 
57.19412994, 57.07357788, 57.00704956, 57.86736679, 58.57844925, 
58.81161118, 58.48048401, 57.68364716, 56.57490921, 56.2657547, 
56.37012863, 56.84865952, 56.8727684, 56.78151703, 56.05365372, 
55.83330917, 55.91601181, 57.18161774, 57.11020279, 57.97662354, 
58.7594223, 57.55088806, 57.38151169, 56.77907562, 56.71346283, 
56.72200775, 57.02871704, 57.20664215, 57.65129471, 56.8236351, 
56.66188431, 57.07388306, 56.72231293, 56.6191597, 56.45527267, 
56.15710831, 56.39484787, 56.58131409, 57.09097672, 57.64488602, 
58.88882065, 57.63847733, 57.26096344, 57.13736343, 56.94265747, 
58.60011292, 58.12555313, 56.57337952, 55.78752899, 55.62517166, 
56.00756836, 55.7924118, 56.04937744, 56.15893936, 56.19403839, 
56.49708557, 57.4040947, 58.07458878, 58.65230179, 59.21170807, 
58.33429718, 57.44468307, 57.40012741, 57.9390831, 57.30796051, 
57.122715, 55.85161972, 55.18631744, 54.35224533, 54.7627182, 
55.6297493, 56.49891663, 57.85485458, 58.17560577, 58.34101486, 
58.48262024, 59.22757721, 59.17660904, 57.99676514, 56.85811996, 
55.34226227, 54.53413391, 54.25946808, 54.94979477, 56.01885986, 
56.9750061, 57.11569595, 56.93930054, 56.67775726, 57.01925659, 
57.87377548, 58.9828186, 59.55656433, 58.72951508, 57.95617676, 
56.83889389, 56.38447189, 56.58375931, 56.63472366, 57.86004257, 
58.03369141, 57.1568985, 55.29618073, 54.50239563, 54.18988419, 
55.19242096, 56.38935471, 57.03512955, 56.98538208, 56.58009338, 
56.73238373, 58.54365921, 59.37437057, 59.96643066, 60.24628448, 
60.03265381, 58.27661896, 56.17786026, 55.68864822, 55.02212524, 
55.76372528, 55.67033768, 55.83117294, 54.42609787, 53.36100388, 
53.37900925, 54.89486313, 57.31650543, 59.9987793, 61.18228531, 
60.41749191, 58.98098755, 57.84600449, 56.96279907, 57.73461151, 
58.54945374, 59.45188904, 58.69807816, 56.38019943, 54.28754425, 
52.30048752, 52.66975784, 54.42884445, 56.63685989, 57.25241852, 
56.61244583, 55.61479568, 55.57633972, 56.72750092, 59.65758133, 
61.70934296, 62.08319092, 60.34150314, 58.17682648, 56.91549301, 
55.86504745, 56.60786819, 57.56187439, 57.49107361, 56.0625, 
53.53587341, 52.23090363, 52.32703781, 54.15845108, 56.52516174, 
58.64772415, 58.89919662, 59.18393707, 59.22208405, 59.08566284, 
59.03775024, 58.72615814, 59.07437515, 58.70815277, 58.16553116, 
56.33716965, 55.15274429, 55.29160309, 54.56159973, 55.22476959, 
55.43473434, 55.32975388, 55.27024078, 55.72100067, 56.59688187, 
56.77693939, 58.28821564, 59.01333618, 59.48454285, 58.7911644, 
58.31507111, 57.65618134, 58.02362061, 58.5058136, 58.1121254, 
57.48161316, 56.83309555, 55.22141266, 54.55641556, 54.56129837, 
54.96902466, 55.65202713, 56.03778458, 56.76351166, 56.33869553, 
56.20807648, 57.21640396, 58.30835724, 59.08841324, 59.30662155, 
59.20346832, 58.48994446, 57.57499695, 57.2450943, 57.02047729, 
56.668293, 56.97927856, 56.6734848, 55.74755096, 54.88051987, 
54.59120178, 55.21866608, 55.86565781, 57.58476639, 57.71050262, 
57.78496552, 57.41233444, 57.20694733, 57.8130455, 58.17987823, 
58.59645462, 58.59828568, 58.00042725, 56.96279907, 56.20715714, 
55.86840439, 55.89770508, 56.11896133, 56.46321106, 56.52058411, 
56.640522, 56.18000031, 56.04449844, 56.62404251, 57.30673981, 
57.51976013, 57.64274979, 57.87438583, 58.27448273, 58.62086868, 
58.61476517, 57.96289063, 57.40439987, 56.20990753, 55.72374725, 
56.23584747, 56.90420151, 56.68569183, 56.39210129, 55.37950134, 
54.38947678, 54.33881378, 55.31480026, 57.0116272, 58.50520325, 
59.58281326, 59.55015564, 58.91781235, 57.70745087, 57.25913239, 
57.93206787, 57.86248398, 57.73674774, 57.43857956, 56.95761108, 
55.80583954, 54.79125595, 54.94293213, 55.37995529, 56.04800415, 
56.7566452, 57.1529274, 57.33497238, 57.13446426, 57.05496597, 
57.34946823, 58.17667007, 59.05514526, 58.64772415, 57.67586136, 
57.15063858, 56.3037529, 55.97887802, 56.88146591, 57.08410645, 
56.97470093, 56.77449799, 55.97079468, 55.06149673, 55.83666611, 
56.17694855, 57.70038223, 58.45179367, 58.18018341, 57.05740738, 
56.18167877, 56.13981628, 57.41141891, 58.16019058, 58.5096283, 
58.02346802, 57.14651871, 56.69896317, 56.32007599, 56.25766754, 
56.71208954, 57.14972305, 56.76381683, 56.60451126, 56.20365143, 
55.78005219, 56.04602051, 56.97470093, 57.57209778, 57.92260361, 
58.10884857, 57.55210876, 57.43873596, 57.37052536, 57.14606094, 
57.30673981, 57.15948868, 56.31412506, 55.79150009, 56.14795303, 
56.75893402, 57.34122849, 56.88604355, 56.64357376, 57.02734375, 
56.44141388, 57.09570694, 57.62230301, 57.93893051, 57.61955643, 
56.78670502, 56.58726883, 56.90389633, 57.32429123, 57.42469788, 
56.92861938, 56.87200546, 56.72063065, 56.48014832, 56.44734192, 
56.68004227, 56.90710449, 57.13690567, 57.79244614, 57.64015579, 
56.75618744, 56.41850281, 56.47846985, 57.50572205, 57.93557358, 
58.89400864, 58.44294357, 57.18237686, 55.8984642, 55.03433228, 
55.47151184, 56.10644913, 57.07281494, 57.96792603, 57.36411667, 
55.68300629, 54.70839691, 54.24771881, 55.80813217, 58.67153168, 
60.64867401, 60.934021, 59.49354553, 57.30292511, 56.55903625, 
56.45848083, 57.37174606, 57.48344421, 57.75200653, 56.67501068, 
55.3546257, 53.99365234, 53.25708771, 53.99456787, 55.34088898, 
57.12073135, 58.32423019, 58.82305145, 58.45042038, 58.35551071, 
58.72646332, 59.13876724, 59.85808945, 59.95269394, 57.96075439, 
56.66112518, 55.82308197, 54.43693542, 54.78973007, 54.78499603, 
55.0871315, 55.49790955, 55.46815491, 55.65477371, 56.0524292, 
56.81493378, 58.20490265, 58.55937195, 58.5460968, 58.80199432, 
59.00753784, 59.55809402, 59.84832382, 59.42640305, 58.16156387, 
55.97903442, 53.99777222, 53.06695557, 53.13241959, 54.00082397, 
55.12161636, 55.89251328, 56.35319138, 56.7972374, 57.58385086, 
59.09039688, 60.27939606, 61.12704849, 60.9060936, 59.82482147, 
57.88582993, 56.80150986, 55.58519363, 55.20676422, 55.30396652, 
55.55207825, 56.01428223, 56.18183136, 55.91525269, 55.78951645, 
55.15152359, 55.36927414, 56.33060455, 56.37989426, 57.33649826, 
57.70897675, 57.85317612, 57.51502991, 57.98883057, 58.51847839, 
59.5986824, 59.49980164, 59.04278564, 57.90841293, 56.74840546, 
55.46337509, 55.34486008, 55.1060524, 55.20691681, 56.02374268, 
55.59907532, 55.4618988, 55.73854828, 55.67094803, 56.49830627, 
57.98699951, 59.25534821, 58.83007431, 58.0780983, 57.78435898, 
58.09640884, 58.45820618, 58.10754776, 58.11243057, 58.18201447, 
56.99804688, 55.72756195, 54.58494949, 54.73891449, 55.26474762, 
55.62761307, 56.86642456, 57.60877228, 57.07388687, 56.5990181, 
57.23593903, 58.02178955, 58.08999634, 58.04345703, 58.01766968, 
57.7800827, 57.8810997, 56.9876976, 56.70048904, 56.56123734, 
56.93914413, 57.12500381, 56.87322617, 56.38889694, 56.0826416, 
56.28406525, 57.12485123, 56.34540558, 56.51387024, 56.59718704, 
56.79861069, 57.50267029, 58.06314087, 58.39533615, 58.0010376, 
57.74681854, 57.73247528, 57.90764999, 57.83929062, 57.41416931, 
56.38355637, 55.45090866, 53.91247177, 53.70647049, 54.51856995, 
57.16757584, 59.36841965, 60.5160675, 59.06552124, 56.72750092, 
55.45594406, 55.757164, 56.62480545, 59.03637695, 59.55229187, 
57.87255478, 55.85512543, 54.07223511, 53.44416809, 55.25772858, 
58.04422379)

Chamber.Lvl.SP <- c(56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.00146484, 56.00146484, 56.00146484, 
56.00146484, 56.00146484, 56.05105209, 56.23700714, 56.42296219, 
56.60891724, 56.79486847, 56.98082352, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017, 56.99942017, 56.99942017, 56.99942017, 56.99942017, 
56.99942017)


```

```{r}


plot(seq(1,length(Chamber.Lvl)), Chamber.Lvl, xlab='Time (min)', ylab='Level (%)', 
     type="l",panel.first = grid() )

```

We see a shift in the mean near minute 1000 and varying degrees of variance throughout the data set. Around the shift, the process seems disturbed. However, the data look relatively clean besides that. Let's look at the other imported vector:

```{r}

plot(seq(1,length(Chamber.Lvl)), Chamber.Lvl.SP, xlab='Time (min)', ylab='Level SP (%)', 
     type="l",panel.first = grid(), ylim=c(52,62) )

```

Great, this probably explains the shift seen in the PV. More conveniently, we have a signal which we can use for detrending the PV time signal.

```{r} 

ts <- 1*60
fs <- 1/ts
fNy <- fs/2

trend <- Chamber.Lvl.SP
x <- (Chamber.Lvl-(trend))*                 #Window the residuals
  hanning.window(length(Chamber.Lvl))

plot(seq(1,length(Chamber.Lvl)), Chamber.Lvl-trend, xlab='Time (min)', ylab='Level SP (%)',
     main = 'Detrended Signal', type="l",panel.first = grid(), ylim=c(-5,5) )

plot(seq(1,length(Chamber.Lvl)), x, xlab='Time (min)', ylab='Level SP (%)',
     main = 'Windowed Signal', type="l",panel.first = grid(), ylim=c(-5,5) )

fft <- fft(x)
fft.y <- Mod(fft)/(length(fft)/2)  #Complex output -> amplitudes
fft.x <- seq(1,length(fft),1)      #Index for x axis


fft.x <- fft.x*fs/length(fft)      #Convert to Hz
fft.x <- fft.x[1:(length(fft)/2)]  #Take only real values
fft.y <- fft.y[1:(length(fft)/2)]  #Take only real values
plot(fft.x, fft.y, xlab='Hz', ylab='Amplitude', main='Chamber Lvl', type="h")

```


We instantly see a surges around .001 and .002 Hz. Also, the entire region below .003 Hz seems to be stronger than the higher frequencies. However, plotting the results against Hz on the order of .001 is not going to be as intuitive as seeing them against a scale of 0 to 30 minutes:

```{r, fig.width=10}
1/head(fft.x,20)/60


  
par(mfrow=c(1,2))
p1 <- plot((1/fft.x/60), fft.y, xlab='Period (min)', ylab='Amplitude', main='Chamber Lvl', type="h", xlim=c(0,30))
p2 <- plot((1/fft.x/60), fft.y, xlab='Period (min)', ylab='', main='Chamber Lvl', type="l", xlim=c(0,30))

```

Note how the plot is less-dense at longer periods. Remember that fs:N dictates the frequency resolution, and not exactly the period resolution. Thus while the frequency axis has regular bins, the period axis is effectively sampled at (uneven) 1/fi intervals. That is why we see large gaps between the longer periods, and the size of the gaps decrease as the size of the periods decrease.

Even with the processing and cleaning performed on the data, the resulting periodogram is noisy. You may already have some ideas on how to make it cleaner, but we would be remiss not to look at the power spectrum if we have alredy come this far: 

```{r}


plot((1/fft.x/60), fft.y**2*.5, xlab='Period (min)', ylab='Power', main='Chamber Lvl', type="h", xlim=c(0,30))


```

We see that some of the features from the last spectrum are pronounced in this one. There seem to be 2 individual spikes, one at 20 minutes and one at 18 miuntes. It could be that these oscillations have the same source but show up differently under different operating conditions. There is also a less consistent, approximately 7 minute period component which was present in our signal. This is a frequency commonly seen in another unit operation at this mill. It is possible that they have similar sources. Some quick estimations of the residence time of the chamber and a trend of the level control loop's valve position with the level shows that the control loop is doing what it can, given the process lag. We should thus look at neighboring process inputs to determine the source of these oscillations if we want to stabilize this operation and reduce downstream boiler variability.

A single frequency spectrum in isolation can't give you very insightful information. However, decomposing a number of hand-picked time signals could reveal common disturbances that weren't noticed by visual inspection. While process knowledge and reasoning will always be the most useful tools you can use, these spectra provide you with an additional lens to view these processes. Also, the cross spectral desnity and coherence of multiple oscillatory time signals can be calculated, allowing information about the lags of each signal's oscillations, and the degrees to which different frequencies are corrleated, to be quickly estimated. 


The previous spectra can be generated in one line of code using R's spectrum fucntion. If you'd like to go this route, be sure to check the documentation and set the parameters appropriately. In this case, the meshing of peaks around .05 Hz / 20 minutes tell us that the span is too heavy.
```{r}
spec <- spectrum(x, log='no',demean=F,detrend=F,span=10)


plot(1/(spec$freq*fs*60), spec$spec, type='l', xlim = c(2,32),
     xlab='Period (min)', ylab='Spectrum', main='Chamber Lvl')



```



## Notes / unfinished
should add section about pwelch, mtm. Also on windowing and dc gain

A stationary data set is one whose statistical properties remain constant. Certainly, this is an idealistic assumption made in the efforts to bridge the gaps between theory and practice. Many statistical methods / calculations are based on the assumption that the data are stationary, or at least can be made approximately stationary by transformations (detrending, differencing)

This may be a decent example for demonstrating aliasing...notice how at the highest sampling frequency, we can pick up all the waves. But even at the lower frequency, aliasing (I believe) makes it seem as if there are more. Some more fine tuning may be required if I want to show the sine waves in the time domain too, as right now they just look ugly (maybe automatically adjusting the limits of the graph)
```{r, echo=FALSE}

inputPanel(
  
  sliderInput("fs", label = "Sampling Frequency (Hz)",
              min = 1, max = 5, value = 1, step = 0.03)
)


renderPlot({
  
f1 <- 1
f2 <- .1
f3 <- 2
fs <- input$fs 
fNy <- fs/2
ts <- 1/fs

t <- seq(by=ts, length.out=1000)
x <- (10*(sin(2*pi*t*f1)) + 5*sin(2*pi*t*f2) + 15*sin(2*pi*t*f3)) 

  plot(t, x, type="l", xlab='Time', ylab='Amplitude')

})

renderPlot({
  
  
f1 <- 1
f2 <- .1
f3 <- 2
fs <- input$fs
fNy <- fs/2
ts <- 1/fs

t <- seq(by=ts, length.out=1000)
x <- (10*(sin(2*pi*t*f1)) + 5*sin(2*pi*t*f2) + 15*sin(2*pi*t*f3)) 

fft <- fft(x)
fft.y <- Mod(fft)
fft.x <- seq(1,length(fft), 1) 
fft.x <- fft.x[1:length(fft)/2]*fs/length(fft)       #Convert bins to frequencies
fft.y <- fft.y[1:length(fft)/2]/(length(fft)/2)       #Scale magnitudes
  plot(fft.x, fft.y, xlab='Freq (Hz)', ylab='Magnitude', type="l")
  
})
```

